Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 hybrid_placement.tex
tweak in Section 6

Based on our experiments with Workloads~\Rmnum{1} and \Rmnum{2}, the ``bullying" behavior is
exhibited when the dragonfly network is configured with random placement and
(progressive) adaptive routing, and there is a large relative gap between the
communication intensity of applications running on the network.
As shown through our experimentation, contiguous placement policies give up too
much in terms of congestion and load balance, and hence are an impractical
solution. Further, running each job with a dedicated routing policy is unrealistic, 
since routing policy is part of system configuration which can not be changed
on the fly upon job submission and the policies of some jobs (adaptive)
will still interfere with others.

%Assigning preferable allocation to each job based on its communication intensity is applicable for the batch scheduler with intelligent job placement policy.

%\TODO{Is this reasonable? So much better}

As a natural extension of our observations, one question that arises is whether
we can combine aspects from both random and contiguous allocation policies in
which each application receives the performance benefits from system load
balancing while avoiding the ``bully'' behavior. As an initial exploration of
that question, we set up a mock hybrid job placement policy, in which less
communication-intensive jobs receive contiguous allocations to avoid the
``bully" effect, while the communication-intensive jobs are allocated randomly
in order to distribute the communication load. For Workload~\Rmnum{1}, this
means AMG gets a contiguous allocation while MultiGrid and CrystalRouter get
random allocations. Note that we do not consider challenges inherent in
designing an allocation policy for production usage, such as backfilling,
reserving large contiguous sets of nodes, determining a metric for
communication intensity, etc., preferring a restricted-scope experiment
looking at the design space of dragonfly allocation policies in light of our experimental
observations.

@@

%\TODO{How's this? Awesome}
These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications. However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations. Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to approach optimal network utilization and application performance in high-radix networks.

>>>>

Based on our experiments with Workloads~\Rmnum{1} and \Rmnum{2}, the ``bully" behavior is
exhibited when the dragonfly network is configured with random placement and
(progressive) adaptive routing, and there is a large gap between the
communication intensity of applications running on the network.
As shown through our experimentation, contiguous placement policies give up too
much in terms of congestion and load balance, hence being an impractical solution. 
Further, running each job with a dedicated routing policy is unrealistic, 
since routing policy is part of system configuration which can not be changed
on the fly upon job submission. 
%and the policies of some jobs (adaptive) will still interfere with others.

As a natural extension of our observations, one question that arises is \emph{whether
we can combine the merits of random and contiguous placement policies in
which each application receives the performance benefits from system load
balancing while avoiding the ``bully'' behavior.} As an initial exploration of
the question, we set up a mock hybrid job placement policy, in which less
communication-intensive jobs receive contiguous allocations to avoid the
``bully" effect, while the communication-intensive jobs are allocated randomly
in order to distribute the communication load. For Workload~\Rmnum{1}, this
means AMG gets a contiguous allocation while MultiGrid and CrystalRouter get
random allocations. Note that we do not consider challenges inherent in
designing an allocation policy for production usage, such as backfilling,
reserving large contiguous sets of nodes, determining a metric for
communication intensity, etc., preferring a restricted-scope experiment
looking at the design space of dragonfly allocation policies in light of our experimental
observations.

@@

%\TODO{How's this? Awesome}
These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications. However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations. Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to achieve optimal network utilization and application performance in high-radix networks.
